%\let\nofiles\relax
\documentclass{article}
\usepackage[top=1.0in,  bottom=1.0in, left = 0.75in, right=0.75in]{geometry}
\usepackage{anyfontsize}
%\makeatletter
%\def\@tablebox#1{\begin{tabular}[t]{@{}c@{}}#1\end{tabular}}
%\makeatother

%\addtolength{\voffset}{-1.5cm}
%\addtolength{\textheight}{1cm}
%\addtolength{\hoffset}{-0.5cm}
%\addtolength{\textwidth}{1cm}
\pdfpagewidth 8.5in
\pdfpageheight 11in
\begin{document}
\newcommand{\HRule}{\rule{\linewidth}{0.2mm}}

%\name{\LARGE{Giulio Zhou}\\}
%\address{1655 Euclid Avenue, Berkeley, CA 94709\\
%giuliozhou8@gmail.com\\
%(925) 997-8192\\}
%\begin{center}
%\noindent
%\textbf{{\LARGE Giulio Zhou}}\vspace{-3.4mm}
%1655 Euclid Avenue, Berkeley, CA 94709\\
%\end{center}
%\fontsize{10.7}{14.4}
%\selectfont

\begin{center}
\textbf{{\LARGE Giulio Zhou}} \\ 
% \textbf{\fontsize{11}{13.2} Email:} giuliozhou8@gmail.com  $|$ \textbf{Website:} giuliozhou.com\\
% \textbf{LinkedIn}: linkedin.com/in/giuliozhou $|$ \textbf{GitHub}: github.com/giulio-zhou\\[2mm]
\textbf{\fontsize{11}{13.2} Email:} giuliozhou8@gmail.com  $|$ \textbf{Website:} giuliozhou.com $|$ \textbf{GitHub}: github.com/giulio-zhou\\[2mm]
\end{center}

%\begin{resume}
%\moveleft\hoffset\vbox{\hrule width\resumewidth height 0.8pt}\smallskip
% \begin{figure}[!htb]
% \minipage{0.35\textwidth}
% \fontsize{10.0}{14.4}
% \selectfont
% \textbf{LinkedIn}: linkedin.com/in/giuliozhou\\[-1.4mm]
% \textbf{Email:} giuliozhou8@gmail.com
% \endminipage
% \minipage{0.3\textwidth}
% \fontsize{22.0}{17.2}
% \selectfont
% \center
% \textbf{{Giulio Zhou}}
% \endminipage
% \minipage{0.35\textwidth}
% \fontsize{10.0}{14.4}
% \selectfont
% \raggedleft
% \textbf{GitHub}: github.com/giulio-zhou\\[-1.4mm]
% \textbf{Phone:} (925) 997-8192
% \endminipage
% \end{figure}

\normalsize
\noindent
\textbf{{\Large Education}}\\[-2mm]
\HRule\\
\textbf{Carnegie Mellon University (Pittsburgh, PA)}
\hfill 08/2017 -- \textit{present} \\
\indent
\textbf{PhD, Computer Science} \\
\vspace{-4mm}

\noindent
\textbf{University of California, Berkeley (Berkeley, CA)}
\hfill 08/2012 -- 12/2016 \\
\indent
\textbf{Bachelor of Arts, Computer Science}  
\hfill{\textbf{GPA: 3.893 / 4.0}}\\
\textit{Relevant Coursework}: Machine Learning, Artificial Intelligence, Computer Vision, Deep Reinforcement Learning, Probability and Random Processes, Operating Systems, Computer Networking, Database Systems.
\\

\noindent
\textbf{{\Large Research Experience}}\\[-2mm]
\HRule\\
\noindent
\textbf{Intel Center for Visual Cloud Systems} (Advisers: Dave Andersen, Michael Kaminsky)
\hfill 08/2017 -- \textit{present}
\begin{itemize}
\vspace{-2.5mm}
\item Work on enabling fine-grained video analysis with minimal human supervision.
\vspace{-2.5mm}
\item Focus on low-shot learning of object detectors in video using ensembling, model distillation, and tracking.
\end{itemize}
\vspace{-2mm}
\indent

\noindent
\textbf{Real-time Intelligent and Secure Execution (RISE) Lab} (Adviser: Joseph Gonzalez)
\hfill 05/2016 -- 12/2016
\begin{itemize}
\vspace{-2.5mm}
\item Worked on Clipper, a system for online, low-latency machine learning model serving.
\vspace{-2.5mm}
\item Benchmarked Clipper's RPC system, demonstrating throughput and latency parity with Tensorflow Serving.
\vspace{-2.5mm}
\item Explored the use of classification and hypothesis testing techniques for online model retraining.
\end{itemize}
\vspace{-2mm}

\noindent
\textbf{Berkeley Artificial Intelligence Research Lab} (Adviser: Stuart Russell)
\hfill 03/2015 -- 12/2016
\begin{itemize}
\vspace{-2.5mm}
\item Worked on sampling algorithms for Bayesian LOGic (BLOG), an open-universe probabilistic modeling language.
\vspace{-6.5mm}
\item Implemented a Gaussian Mixture Model (with temporal and spatial constraints) for background subtraction that achieves comparable accuracy to OpenCV's
      state-of-the-art background subtraction libraries. Submitted as part of DARPA's Probabilistic Programming for Advancing Machine Learning (PPAML) program.
\end{itemize}
% \vspace{-2mm}
% 
% \noindent
% \textbf{Nanocrystal Synthesis Lab}
% \hfill 01/2014 -- 12/2014
% \begin{itemize}
% \vspace{-2.5mm}
% \item Ran experiments on the NERSC supercomputers, using gradient descent optimization and the generalized moments method to simulate the optical and mechanical properties of tetrapod nanocrystals.
% \vspace{-2.5mm}
% \item Implemented a 3D lattice-spring model (with Java multithreading) to simulate polymer stress-strain effects.
% \end{itemize}

\noindent
\textbf{\Large Publications}\\[-2mm]
\HRule\\
\noindent
\textbf{Clipper: A Low-Latency Online Prediction Serving System} \\
Daniel Crankshaw, Xin Wang, \textbf{Giulio Zhou}, Michael J. Franklin, Joseph E. Gonzalez, Ion Stoica. \\
USENIX Symposium on Networked Systems Design and Implementation (NSDI), 2017. \\
\vspace{-3mm}

\noindent
\textbf{EDF: Ensemble, Distill, and Fuse for Easy Video Labeling} (\textit{Under Submission}) \\
\textbf{Giulio Zhou}, Subramanya R. Dulloor, David G. Andersen, Michael Kaminsky. \\
\vspace{-3mm}

\noindent
\textbf{Scaling Video Analytics on Constrained Edge Nodes} (\textit{Under Submission}) \\
Christopher Canel, Thomas Kim, \textbf{Giulio Zhou}, Conglong Li, Hyeontaek Lim, David G. Andersen, Michael Kaminsky, Subramanya R. Dulloor. \\

\noindent
\textbf{{\Large Industry Experience}}\\[-2mm]
\HRule\\
\textbf{Google Inc., Keyboard} (Software Engineer)
\hfill 03/2017 -- 08/2017\\
\begin{itemize}
\vspace{-6.5mm}
\item Created infrastructure to support analytics data pipelines and interactive data visualization.
\vspace{-2.5mm}
\item Automated the generation, management and evaluation of Google Keyboard test sets.
\end{itemize}
\vspace{-2mm}

\noindent
\textbf{Google Inc., Display Ad Automation} (Software Engineering Intern)
\hfill 05/2015 -- 08/2015\\
\begin{itemize}
\vspace{-6.5mm}
\item Designed and built a backend pipeline for automated text-to-image matching for internationalized display ads.
\end{itemize}
\vspace{1mm}

\noindent
\textbf{{\Large Teaching Experience}}\\[-2mm]
\HRule\\
\hspace*{1.2mm}\textbf{CS 189/289A: Introduction to Machine Learning} (Fall 2016) \\
\vspace{0.5mm}
\textbf{CS 61BL: Data Structures and Programming Methodology} (Summer 2016) \\
\vspace{0.5mm}
\textbf{CS 61B: Data Structures and Algorithms} (Spring 2016)
\vspace{2.0mm}

% \noindent
% \textbf{{\Large Teaching Experience}}\\[-2mm]
% \HRule\\
% \textbf{CS 189/289A, Introduction to Machine Learning (Fall 2016)}
% \begin{itemize}
% \vspace{-2.5mm}
% \item Taught undergraduate and graduate students in two weekly 1-hour discussions, covering topics such as support vector machines, bias-variance tradeoff, classifiers, logistic regression, kernelization, and neural networks.
% \end{itemize}
% \vspace{-2mm}
% \textbf{CS 61BL, Data Structures and Programming Methodology (Summer 2016)}
% \begin{itemize}
% \vspace{-2.5mm}
% \item Prepared daily mini-lectures, developed course material and led 12 hours of laboratory instruction per week.
% \end{itemize}
% \vspace{-2mm}
% \textbf{CS 61B, Data Structures and Algorithms (Spring 2016)}
% \begin{itemize}
% \vspace{-2.5mm}
% \item Held office hours, wrote exam problems and led weekly discussion and laboratory sections.
% \vspace{-2.5mm}
% \item Led the CS Scholars section, comprised primarily of students with little to no background in computer science and from typically underrepresented demographic groups. Taught a weekly seminar devoted to academic success and career development.
% \end{itemize}
\pagenumbering{gobble}

\newpage
\noindent
\textbf{{\Large Organizations}}\\[-2mm]
\HRule\\
\textbf{Tau Beta Pi, Engineering Honor Society} \\
\textbf{Information Technology Chair}
\hfill 01/2015 -- 05/2016
\begin{itemize}
\vspace{-2.5mm}
\item Oversaw a 4-member team in Django full-stack development, maintaining a strict code review system and requiring comprehensive unit-testing and style adherence.
\vspace{-2.5mm}
\item Led the development and deployment of the Tau Beta Pi Alumni Database, connecting Tau Beta Pi members to alumni mentors throughout industry and academia.
\vspace{-2.5mm}
\item Coordinated Tau Beta Pi website hackathons, where participants work in teams on novel website features; notable projects include search autocompletion, Alumni Database prototype, and tools for website analytics.
\end{itemize}
\vspace{-3.0mm}

\noindent
\textbf{Professional Development Officer}
\hfill 09/2014 -- 12/2014
\begin{itemize}
\vspace{-2.5mm}
\item Held mock interviews and critiqued resumes for the engineering community.
\vspace{-2.5mm}
\item Coordinated workshops on Analytical Problem Solving, People Skills and Cultural Awareness.
\end{itemize}
\vspace{-3.0mm}

\noindent
\textbf{Member}
\hfill 05/2014 - \textit{present}
\begin{itemize}
\vspace{-2.5mm}
\item Tau Beta Pi accepts the top 25\% seniors in the College of Engineering.
\end{itemize}
\vspace{-1.5mm}

\noindent
\textbf{EECS Honors Degree Program} \\
\textbf{Member}, \textit{Concentration in Chemical Engineering}
\hfill 01/2015 - \textit{present}
\begin{itemize}
\vspace{-2.5mm}
\item Honors Program with 20-30 students. Requirements include research and extended studies in concentration outside EECS.
\end{itemize}
% \vspace{1mm}
% \begin{itemize}
% \vspace{-1.8mm}
% \item Tau Beta Pi accepts the top 25\% seniors in the College of Engineering
% \end{itemize}
% \noindent
% \textbf{Alpha Chi Sigma, Professional Chemistry Fraternity} \\
% \textbf{Webmaster}
% \hfill 09/2014 -- 12/2014
% \begin{itemize}
% \vspace{-1.8mm}
% \item 
% \end{itemize}

% \noindent
% \textbf{\Large Projects}\\[-2mm]
% \HRule\\
% \textbf{Automatic Panorama Generator} 
% \begin{itemize}
% \vspace{-1.8mm}
% \item Given source images, runs adaptive feature point detection and RANSAC outlier elimination, then learns a homography transformation matrix via least squares
% \end{itemize}
% \vspace{-1.8mm}
% \noindent
% \textbf{Convolutional Neural Networks for Image Compression Artifact Removal}
% \begin{itemize}
% \vspace{-1.8mm}
% \item Trained a deep convolutional neural network to remove JPEG compression artifacts
% \vspace{-2.5mm}
% \item Optimized training using Xavier weight initialization, dropout and fine tuning in the final layer
% \end{itemize}

\noindent
\textbf{\Large Technical Skills}\\[-2mm]
\HRule\\
\textbf{Programming Languages:} Python, Java, C, C++, Rust, \LaTeX \\
\textbf{Software/Frameworks:} Caffe, Tensorflow, OpenCV, Apache Spark, Hadoop MapReduce

\pagenumbering{gobble}
%\end{resume}
\end{document}
